Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-09 rebuttal.tex

\comment{p1, c1, l32: I think the phrase miracle molecule could be
  more usefully replaced with new drugs or new small molecule
  therapeutics.}
\response{The text has been updated to use the term ``therapeutic
  molecule''}

\comment{P4, c2, l41: the GDB-13 database contains 970 million
  molecules, which is nearly a billion, not a trillion.}
\response{The text has been updated to use the correct number}

\comment{P5, c1, l29: the normal phrase used to describe this concept
  is the similar property principle. The authors should also provide a
  reference.}
\response{This portion of the text has been restructured to refer to
  the similarity property principle and also include the relevant
  reference}

\comment{P5, c1, l40: QSAR should be referenced to Hansch et al. Also
  perhaps some discussion on what the authors mean by referring to
  these approaches as traditional.}
\response{We have updated text to include references to Hansch and
  Free \& Wilson. Regarding the use of ``traditional'', we believe the
  text explicitly explains why - the fact that QSAR as originaly
  defined only considers ligand features. However, we have rephrased it to use
  ``traditionally'' since one can argue that methods such as docking
  and pharmacophores are also QSAR methods, but consider both ligand
  and receptor.}

@@

\comment{P5, c2, l42: formal citation for one of Hopfinger?s papers is
  required here.}
\response{The relevant reference has been added}

\comment{P5, c2, l58: this assertion is made with no evidence to back
  it up. Why should multi-target models be more reliable? It is not
  clear to me that they should.}\marginpar{\textbf{Needs more work}}
\response{We have rephrased this statement to be less dogmatic}

\comment{P7, c2, l51: why is chemically in inverted commas and not
  algorithmically? I would prefer inverted commas for neither.}
\response{Quotes have been removed}

\comment{P8, c1, l10: ELN's should be ELNs.}
\response{Corrected}
\end{document}

### 2011-11-09 paper.tex
some minor changes. added review comments doc to repo

\begin{figure}
\centering
\includegraphics[height=2in]{chemical-structures.png}
\caption{The many different facets of representing chemical structures. Shown
are a chemist's usual representation of a molecule (top left) and a
graph-based representation amenable to data mining (top right). These
representations are supplemented by a 3D representation of the same molecule
(bottom left) that is closer to reality and a representation using surface
properties (bottom right), which is often more relevant for the properties the
molecule exhibits in an experimental setup (such as when measuring its
solubility, or bioactivity).}
\label{figure:chemical-structures}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=1in]{lipoicacid.png}
\caption{The standard chemical graph illustration together with the SMILES, InChI and InChIKey codes for lipoic acid. Note that the SMILES is much more human-readable than the others.}
\label{figure:smiles}
\end{figure}

@@

In 2010, drug company Glaxo made public over 13,000 compounds that they have investigated as potential cures for malaria~\cite{glaxo-malaria}.  (Malaria has traditionally been a ``neglected'' disease in drug research, because the populations who suffer from it tend not to have enough money to be a stable consumer base for a new pharmaceutical.)  Perhaps we will now be able to find cures for some of these neglected diseases, by using the open source, open data approach to the computer science of chemical discovery.

@@

\begin{figure}
\includegraphics[height=1.3in]{platins.png}
\caption{The generated InChI is the same for the stereoisomers cisplatin and transplatin.}
\label{figure:cistrans}
\end{figure}
\begin{figure}
\includegraphics[height=2in]{CACM_ApplicabilityDomain.pdf}
\caption{Illustration of the ``Applicability Domain'' concept. In order to estimate whether model predictions are reliable, it is crucial to define areas of ``chemical space'' where the model is applicable, and where it is not. In this case, the ``model domain'' includes the molecule at the top. The (relatively similar) molecules to the left are likely to be included in the Applicability Domain of the model, while the (more dissimilar) molecules to the right are likely located outside this domain, hence the generated model is probably not applicable.}
\label{figure:applicability-domain}
\end{figure}

>>>>

% \begin{figure}
% \centering
% \includegraphics[height=2in]{chemical-structures.png}
% \caption{The many different facets of representing chemical structures. Shown
% are a chemist's usual representation of a molecule (top left) and a
% graph-based representation amenable to data mining (top right). These
% representations are supplemented by a 3D representation of the same molecule
% (bottom left) that is closer to reality and a representation using surface
% properties (bottom right), which is often more relevant for the properties the
% molecule exhibits in an experimental setup (such as when measuring its
% solubility, or bioactivity).}
% \label{figure:chemical-structures}
% \end{figure}

@@

% \begin{figure}
% \centering
% \includegraphics[height=1in]{lipoicacid.png}
% \caption{The standard chemical graph illustration together with the SMILES, InChI and InChIKey codes for lipoic acid. Note that the SMILES is much more human-readable than the others.}
% \label{figure:smiles}
% \end{figure}

@@

In 2010, drug company Glaxo made public over 13,000 compounds that
they have investigated as potential cures for
malaria~\cite{glaxo-malaria}.  (Malaria has traditionally been a
neglected disease in drug research, because the populations who
suffer from it tend not to have enough money to be a stable consumer
base for a new pharmaceutical.)  Perhaps we will now be able to find
cures for some of these neglected diseases, by using the open source,
open data approach to the computer science of chemical discovery.

@@

% \begin{figure}
% \centering
% \includegraphics[height=1.3in]{platins.png}
% \caption{The generated InChI is the same for the stereoisomers cisplatin and transplatin.}
% \label{figure:cistrans}
% \end{figure}
% %
% \begin{figure}
% \centering
% \includegraphics[height=2in]{CACM_ApplicabilityDomain.pdf}
% \caption{Illustration of the ``Applicability Domain'' concept. In order to estimate whether model predictions are reliable, it is crucial to define areas of ``chemical space'' where the model is applicable, and where it is not. In this case, the ``model domain'' includes the molecule at the top. The (relatively similar) molecules to the left are likely to be included in the Applicability Domain of the model, while the (more dissimilar) molecules to the right are likely located outside this domain, hence the generated model is probably not applicable.}
% \label{figure:applicability-domain}
% \end{figure}
% %
